Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-15 sections/theoretical.tex
Changed Figure references to match new Figure I also fixed a spelling mistake
Updating geometry figure
The text in the figure wasn't filled in, so it looked bad. I've
updated it so that the text looks better
Changed graph sizes to 0.6 to fit.

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, as shown in Figure \ref{fig:OpticalLightcurveComparison}, validating our optical eclipse lightcurve.

@@

\begin{figure}
\begin{minipage}{0.49\textwidth}
  \includegraphics[width=0.6\textwidth]{figures/drawing}
  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun. The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi r_\odot^2$}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
\begin{equation}\label{eq:geometry_1}
  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
\end{equation}
\begin{equation}\label{eq:geometry_2}
  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
\end{equation}
\begin{equation}\label{eq:geometry_3}
  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
\end{equation}
\begin{equation}\label{eq:geometry_4}
  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
\end{equation}
\end{minipage}
\end{figure}

\begin{figure}
  \includegraphics[width=0.75\textwidth]{figures/RadiovsTheoretical}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}

>>>>

In order to check the validity of our livestream-derived optical lightcurve, we needed a way of finding the expected eclipse obscuration percentage over time for our location.
We used the free, open-source planetarium software \texttt{Stellarium}\cite{zotti_simulated_2020} to achieve this.
After setting the time, date and location of our radio telescope in \texttt{Stellarium}, we queried the software's API to step the simulation time forward and extracted the eclipse percentage for 1000 points in time, starting before first contact and ending after fourth contact.
The resulting theoretical lightcurve was then overlaid on the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, as shown in Figure \ref{fig:LightcurveComparison}, validating our optical eclipse lightcurve.

@@

\begin{figure}
\begin{minipage}{0.49\textwidth}
  \includegraphics[width=0.6\textwidth]{figures/drawing_updated}
  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun. The percent obscuration is found by dividing the combined area $A_1 + A_2$ by the apparent area of the sun's disk $\pi R_\odot^2$}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
\begin{equation}\label{eq:geometry_1}
  A_1 = \frac{1}{2}r_{\odot}^2\left(\phi_1 - \sin\phi_1\right)
\end{equation}
\begin{equation}\label{eq:geometry_2}
  A_2 = \frac{1}{2}r_{m}^2\left(\phi_2 - \sin\phi_2\right)
\end{equation}
\begin{equation}\label{eq:geometry_3}
  \phi_1 = 2\cos^{-1}\left(\frac{r_{\odot}^2 - r_{m}^2+x^2}{2r_{\odot}x}\right)
\end{equation}
\begin{equation}\label{eq:geometry_4}
  \phi_2 = 2\cos^{-1}\left(\frac{x^2 - r_{\odot}^2 + r_{m}^2}{2r_{m}x}\right)
\end{equation}
\end{minipage}
\end{figure}

\begin{figure}
  \includegraphics[width=0.6\textwidth]{figures/RadiovsTheoretical}
  \caption{\label{fig:RadiovsTheoretical} A comparison of the smoothed/normalized radio lightcurve and theoretical lightcurves generated with the JPL Horizons ephemeris data.}
\end{figure}
